Safety judges are increasingly used as moderation infrastructure, yet ordinary harmfulness or jailbreak metrics do not isolate whether the same safety case receives a different label when wrapped in social pressure. We introduce \auditname, a Matched-Neutral Safety-Label Audit protocol for measuring pressure-specific label sensitivity with a matched-neutral estimand: the underlying case and gold label are fixed, pressure attacks are compared with neutral controls matched by base case, layout, and format, and inference is over bases rather than rendered prompts. This is a protocol-bounded audit contribution, not a first demonstration that judge models can be artifact-sensitive. The protocol contributes a base-level estimand, artifact ledger, and fail-closed claim gate. \method is evaluated only as a diagnostic matched-control readout for residual-gap accounting under the same contract. On the frozen 50-base \auditname gate, DynaGuard and WildGuard show supported raw pressure vulnerabilities, while BingoGuard and HarmAug serve as raw-vulnerability-not-supported guardrails. The diagnostic readout makes the DynaGuard and WildGuard residual gaps unsupported in this gate; F1 is only a non-degradation sanity check. Projection ablations show that arbitrary global or other-base neutral replacement fails, while same-base controls can also attenuate the gap. As a secondary offline mitigation replay, a neutral-consensus selective wrapper descriptively reduces measured error on auto-decided attack subsets while explicitly reporting abstention and induced-error costs. PKU200, PKU2K full-data, and non-PKU200 diagnostics address sample-size concerns by replicating raw vulnerabilities and strong attenuation beyond the selected 50-base artifact, but mean-v1 residual evidence can remain statistically supported at larger scale; scale-up therefore supports replication plus attenuation only, not residual elimination, source-general robustness, or a replacement primary claim gate.
