\section{Conclusion}

This work operationally isolates social pressure as a paired nuisance factor for safety judges under an authored matched-neutral contract and contributes an audit protocol around a matched-neutral safety-label estimand, base-level inference unit, and fail-closed evidence-to-claim gate. Under the frozen 50-base \auditname contract, DynaGuard and WildGuard exhibit supported raw pressure vulnerabilities, while BingoGuard and HarmAug act as raw-vulnerability-not-supported guardrails. The independent primary sample size for the main claim is 50 bases, and the conclusion is a selected-baseline claim under this frozen gate. \method is only a diagnostic matched-control readout: in the 50-base gate it makes the DynaGuard and WildGuard residual gaps unsupported, yields Holm-adjusted positive paired attenuation, and passes the ordinary F1 non-degradation check for all selected main baselines. A secondary neutral-consensus selective-wrapper replay descriptively reduces measured error on auto-decided subsets while exposing abstention and induced-error costs, but this remains an offline multi-query mitigation diagnostic. The PKU200, PKU2K full-data, and non-PKU200 diagnostics replicate raw vulnerabilities and strong attenuation, while also showing that mean-v1 residual evidence can remain supported at larger scale. Thus scale-up evidence is replication plus attenuation only, not residual elimination, source-general robustness, or a replacement for the frozen gate. The projection ablations further clarify what is and is not new: base-matched controls matter, arbitrary neutral replacement fails, and the exact estimator should not be oversold as uniquely optimal. The result is intentionally bounded: the evidence supports a matched-control audit conclusion, not equal-cost deployment, source-general robustness, single-pass robustness, or deployable-model superiority.
